Component response rate variation drives stability in large complex systems

### 2018-05-25 notebook/SI.Rmd
Add more to rework the project

```{r, echo = FALSE}
cdat   <- read.csv(file = "sim_results/ecology/competition_C_1.csv");
cdat   <- cdat[,-1];
cd_tab <- cdat[,1:7];
kable(cd_tab);
```

@@

```{r, echo = FALSE}
mdat   <- read.csv(file = "sim_results/ecology/mutualism_C_1.csv");
mdat   <- mdat[,-1];
md_tab <- mdat[,1:7];
kable(md_tab);
```

@@

```{r, echo = FALSE}
pdat   <- read.csv(file = "sim_results/ecology/pred-prey_C_1.csv");
pdat   <- pdat[,-1];
pd_tab <- pdat[,1:7];
kable(pd_tab);
```

>>>>

```{r}
data(ecology);
```

```{r, echo = FALSE}
cd_tab <- cdat[,1:7];
kable(cd_tab);
```

@@

```{r, echo = FALSE}
md_tab <- mdat[,1:7];
kable(md_tab);
```

@@

```{r, echo = FALSE}
pd_tab <- pdat[,1:7];
kable(pd_tab);
```
